MsCcHSFeed Outline

### 2022-02-17 MsCcHSFeedOutlineDec15.Rmd
Made a new Fig 2 with Joel's suggestions, saved the other figures to the repo

@@

ggsave("~/Desktop/waspplot.png", plot = waspplot, width = 8, height = 5)

@@

ggsave("~/Desktop/violins2.png", violins, width = 8, height = 5)

@@

ggsave("~/Desktop/outcomesdead.png", plot = barsdead, width = 8, height = 5)
```

@@

ggsave("~/Desktop/newmeans.png", newmeans, width = 8, height = 5)
```

@@

ggsave("~/Desktop/newarea.png", newarea, width = 8, height = 5)
```

>>>>

```{r}
datawasp2 <- datawasp %>%
  gather(stage, number, num.w.tot, num.w.eclos)

datawasp2$stage <- gsub("num.w.", "", datawasp2$stage)
datawasp2$stage <- gsub("tot", "Emerged", datawasp2$stage)
datawasp2$stage <- gsub("eclos", "Eclosed", datawasp2$stage)

datawasp2 <- datawasp2 %>%
  select(ID, food, treatment, stage, number)

waspmeans <- summarySE(datawasp2, measurevar = "number", groupvars = c("food", "treatment", "stage"))
waspmeans$stage <- factor(waspmeans$stage, levels = c("Emerged", "Eclosed"))
waspmeans$comb <- paste(waspmeans$food, waspmeans$treatment, sep = " ")
```

```{r}
newwaspplot <- ggplot(data = waspmeans, aes(x = stage, y = number, group = comb, color = treatment)) + 
  theme_bw() + 
  geom_line(aes(linetype = food)) + 
  geom_point(aes(shape = food), size = 3) + 
  geom_errorbar(aes(ymin = number - se, ymax = number + se), size = 0.25, width = 0.2) + 
  scale_linetype_manual(values = c("dashed", "solid")) + 
  scale_shape_manual(values = c(1, 19)) + 
  labs(x = "Wasp Developmental Stage", y = "Number of wasps per caterpillar host", shape = "Hostplant", 
       linetype = "Hostplant", color = "Treatment")

newwaspplot

ggsave("~/Desktop/GitHub/MsCcHSFeed/Figs/newwaspplot.png", newwaspplot, width = 8, height = 5)
```

@@

ggsave("~/Desktop/GitHub/MsCcHSFeed/Figs/waspplot.png", plot = waspplot, width = 8, height = 5)

@@

ggsave("~/Desktop/GitHub/MsCcHSFeed/Figs/violins2.png", violins, width = 8, height = 5)

@@

ggsave("~/Desktop/GitHub/MsCcHSFeed/Figs/outcomesdead.png", plot = barsdead, width = 8, height = 5)
```

@@

ggsave("~/Desktop/GitHub/MsCcHSFeed/Figs/newmeans.png", newmeans, width = 8, height = 5)
```

@@

ggsave("~/Desktop/GitHub/MsCcHSFeed/Figs/newarea.png", newarea, width = 8, height = 5)
```
